### 2023-06-02 resilience.tex
up

% \alain{dessous: à dire mais pas sous forme de proposition}
\begin{remark}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
\end{remark}
\alain{parfois $\mathscr{S}=(S,\rightarrow,\leq)$ is
(\Bad,\Safe)-resilient parfois $\mathscr{S}=(S,\rightarrow,\leq)$ is 
(\Safe,\Bad)-resilient , rendre cohérent avec $\mathscr{S}=(S,\rightarrow,\leq)$ is
(\Bad,\Safe)-resilient}

>>>>

\begin{remark}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Safe, \Bad)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Safe, \Bad)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
\end{remark}
